The Name of the Title is Hope

### 2024-04-03 input/2_introduction.tex

Advances in hardware that augment a user's physical actions have reignited dreams of overcoming human limitations, recovering lost abilities and simplifying skill acquisition~\citep{Goto2020-mw, Kunze2017-co}. These technological advances include the miniaturization of the actuating hardware to wearable form factors and the direct sensing and stimulation capabilities of neural interfaces. Especially due to these characteristics, recent perspectives promote a change of the computing era from human-computer \textit{interaction} to \textit{integration}~\cite{Mueller2020-dl}. One key change in perspective is, that \textit{integrated} users share agency with the computing machinery to execute tasks. This is a critical distinction as \textit{integration} technologies are designed to directly influence people’s bodies, their actions, and the resulting action outcomes.

@@

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=\columnwidth]{figures/teaser_new.png}%{figures/bci_game.png}
    \caption{Our augmentation system: When participants feel the spontaneous urge to move, readiness potentials (RPs) are picked up in the user's brain signals. A brain-computer interface (BCI) predicts the data to be in either of two classes: Idle or pre-movement. In the latter case, electrical muscle stimulation (EMS) is triggered and the user's hand is moved. Image taken with consent from participant.}
\end{figure}

@@

Upon predicting a \textit{pre-movement} state, the system augmented the user's action, potentially preceding their voluntary motor command. This augmentation moved the ring finger in accordance with the user's intention to act. We achieved the movement by leveraging electrical muscle stimulation (EMS) applied to the user's forearm flexor muscle. In our user study, a mixed-methods research approach was employed to explore whether aligning the physical impact on the user's body with their intention to move preserved their SoA.

>>>>

Advances in hardware that augment a user's physical actions have reignited dreams of overcoming human limitations, recovering lost abilities and simplifying skill acquisition~\citep{Goto2020-mw, Kunze2017-co}. These technological advances include the miniaturization of the actuating hardware to wearable form factors and the direct sensing and stimulation capabilities of neural interfaces. Especially due to these characteristics, recent perspectives promote a change of the computing era from human-computer \textit{interaction} to \textit{integration}~\cite{Mueller2020-dl}. One key change in perspective is, that \textit{integrated} users share agency with the computing machinery to execute tasks. This is a critical distinction as \textit{integration} technologies are designed to directly influence people’s bodies, their actions, and the resulting action outcomes~\cite{Cornelio2022-aq}.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\columnwidth]{figures/teaser.png}%{figures/bci_game.png}
    \caption{We propose an augmentation system that maintains agency. When participants feel the spontaneous urge to move, readiness potentials (RPs) are picked up in the user's brain signals. A brain-computer interface (BCI) then predicts the user to be in either an idle (red) or pre-movement (green) state. In the latter case, electrical muscle stimulation (EMS) is triggered and the user's hand is moved. Image taken with consent from participant.}
\end{figure}

@@

% \begin{figure}[!h]
%     \centering
%     \includegraphics[width=\columnwidth]{figures/teaser_new.png}%{figures/bci_game.png}
%     \caption{Our augmentation system: When participants feel the spontaneous urge to move, readiness potentials (RPs) are picked up in the user's brain signals. A brain-computer interface (BCI) predicts the data to be in either of two classes: Idle or pre-movement. In the latter case, electrical muscle stimulation (EMS) is triggered and the user's hand is moved. Image taken with consent from participant.}
% \end{figure}

@@

Upon predicting a \textit{pre-movement} state, the system augmented the user's action, potentially even preceding their voluntary motor command. This augmentation moved the ring finger in accordance with the user's intention to act. We achieved the movement by leveraging electrical muscle stimulation (EMS) applied to the user's forearm flexor muscle. To get a first glimpse of how our system can maintain agency in augmented users, we conducted a user study using a mixed-methods research approach. In short, we explored whether aligning the physical impact on the user's body with their intention to move preserved their SoA.
